Compare pseqs

### 2019-05-20 comparepseqs.Rmd
Lapply to for

@@

    if("clean" %in% names(args)) {
        unlink("rds-comparepseqs", recursive=TRUE)
        unlink("cache", recursive=TRUE)
    }
    if ("loadlast" %in% names(args) )
        load(paste0("session/", sort(list.files("session"), decreasing = TRUE)[1]))
}
```

@@

@@

```{r data}
pseq = list()
pseq$shogun <- import_filter_data("data/phfinrisk_species_all_drop50k_2018-12-21.RDs")
pseq$R16S <- import_filter_data("data/phfinrisk_16S_otu_raw_2019-02-19.RDs")
pseq$gtdb <- import_filter_data("data/phfinrisk_gtdb_species_all_drop50k_2019-01-14.RDs")
pseq$ncbi <- import_filter_data("data/phfinrisk_custom70_species_all_2019-01-29.RDs")
pseq$centrifuge <- import_filter_data("data/phfinrisk_centrifuge_species_all_2018-11-30.RDs",
                                      excluded = c("DIAB"))
```

```{r alpha diversities}
dset <- mclapply(pseq, function(x) meta.merge.alphadiversity(x) %>%
                                             mutate(diversities_shannon = scale(diversities_shannon)),
                           mc.cores = length(pseq))

fo.alpha.min <- "%s ~ BL_AGE + SEX  + diversities_shannon"
fo.alpha.full <- "%s ~ BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + BL_USE_RX_C03 + BL_USE_RX_C07 + BL_USE_RX_C08 + BL_USE_RX_C09 + diversities_shannon" # MISSING DIAB

alphadiversity <-  mclapply(dset, function(x)
    list(min =  calculateglm(x, modelstring = fo.alpha.min),
         full = calculateglm(x, modelstring = fo.alpha.full)),
    mc.cores = length(pseq))
```

```{r dissimilarity matrix}
if (!file.exists("rds-comparepseqs/comparepseqs_bray_matrix.rds")) {
    bray.dist.matrix <- mclapply(pseq, function(x) calculate.beta.matrix(x), mc.cores = length(pseq))
    saveRDS(bray.dist.matrix, file = "rds-comparepseqs/comparepseqs_bray_matrix.rds")
} else {
    bray.dist.matrix  <- readRDS("rds-comparepseqs/comparepseqs_bray_matrix.rds")
}
```

 ```{r adonis calculation}
if (!file.exists("rds-comparepseqs/beta.diversity.rds")) {

    covariates.min <- c("BL_AGE", "SEX")
    covariates.full <- c("BL_AGE", "SEX", "BMI", "CURR_SMOKE",
                         "Q57X", "BL_USE_RX_C03", "BL_USE_RX_C07",
                         "BL_USE_RX_C08", "BL_USE_RX_C09")

    betadiversity <- mclapply(c2l(names(pseq)), function(x)
        list(min = calculateadonis(dset = meta(pseq[[x]]),
                                   matrix = bray.dist.matrix[[x]],
                                   covariates = covariates.min,
                                   npermutations = 1000),
             full = calculateadonis(dset = meta(pseq[[x]]),
                                    matrix = bray.dist.matrix[[x]],
                                    covariates = covariates.full,
                                    npermutations = 1000)),
        mc.cores = length(pseq))

     saveRDS(betadiversity, file = "rds-comparepseqs/beta.diversity.rds")
    } else {
     betadiversity <- readRDS("rds-comparepseqs/beta.diversity.rds")
}
```

@@

>>>>

```{r packrat, include = FALSE, eval = FALSE}
packrat::opts$ignored.packages(c("Maaslin", "finriskmetagcommon", "biomformat",
                                 "microbiome", "phyloseq" ))
packrat::snapshot()
```

@@

    if("clean" %in% names(args)) {
        unlink("rds-comparepseqs", recursive=TRUE)
        unlink("cache", recursive=TRUE)
    }
    if ("loadlast" %in% names(args) )
        load("session/comparepseqs.Rdata")
}
```

@@

```{r install, eval = FALSE, include = FALSE}
source("https://bioconductor.org/biocLite.R")
biocLite("BiocInstaller")
library(BiocInstaller)
source("http://www.bioconductor.org/biocLite.R")
biocLite("microbiome")
```

@@

#         "data/phfinrisk_16S_otu_raw_2019-02-19.RDs",
     #         "data/phfinrisk_gtdb_species_all_drop50k_2019-01-14.RDs",
     #         "data/phfinrisk_custom70_species_all_2019-01-29.RDs",

```{r constants}
fo.alpha.min <- "%s ~ BL_AGE + SEX  + diversities_shannon"
fo.alpha.full <- "%s ~ BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + BL_USE_RX_C03 + BL_USE_RX_C07 + BL_USE_RX_C08 + BL_USE_RX_C09 + diversities_shannon" # MISSING DIAB

covariates.min <- c("BL_AGE", "SEX")
covariates.full <- c("BL_AGE", "SEX", "BMI", "CURR_SMOKE",
                         "Q57X", "BL_USE_RX_C03", "BL_USE_RX_C07",
                         "BL_USE_RX_C08", "BL_USE_RX_C09")
```

```{r rds files}
rds <- list("shogun" = "data/phfinrisk_species_all_drop50k_2018-12-21.RDs",
            "centrifuge" = "data/phfinrisk_centrifuge_species_all_2018-11-30.RDs")
```

```{r models}
ret <- list()

for (key in names(rds)) {
    pseq <- import_filter_data(rds[[key]] ,excluded = c("DIAB"))
    dset <- meta.merge.alphadiversity(x) %>%
        mutate(diversities_shannon = scale(diversities_shannon))

    alphadiversity <- list(min =  calculateglm(x, modelstring = fo.alpha.min),
                           full = calculateglm(x, modelstring = fo.alpha.full))

    saveRDS(alphadiversity,
            file = paste0("rds-comparepseqs/alpha-", key , ".rds"))

    bray.dist.matrix <- calculate.beta.matrix(pseq)

    betadiversity <- list(min = calculateadonis(dset = dset,
                                                matrix = bray.dist.matrix,
                                                covariates = covariates.min,
                                                npermutations = 1000),
                          full = calculateadonis(dset = dset,
                                                 matrix = bray.dist.matrix,
                                                 covariates = covariates.full,
                                                 npermutations = 1000))

    saveRDS(betadiversity,
            file = paste0("rds-comparepseqs/alpha-", key , ".rds"))

    ret[[key]] = list("alphadiversity"  = alphadiversity,
                      "betadiversity" = betadiversity)
}
```

@@

betadiversity

ls()
